%------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------------

\documentclass[DIV=calc, BCOR=5mm, paper=a4, fontsize=11pt, twocolumn]{scrartcl}	 % A4 paper and 11pt font size

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[english]{babel} % English language/hyphenation
\usepackage[protrusion=true,expansion=true]{microtype} % Better typography
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage[svgnames]{xcolor} % Enabling colors by their 'svgnames'
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{fix-cm}	 % Custom font sizes - used for the initial letter in the document
\usepackage{setspace}

\usepackage{sectsty} % Enables custom section titles
\allsectionsfont{\usefont{OT1}{phv}{b}{n}} % Change the font of all section commands

\usepackage{fancyhdr} % Needed to define custom headers/footers
\pagestyle{fancy} % Enables the custom headers/footers
\usepackage{lastpage} % Used to determine the number of pages in the document (for "Page X of Total")

% Headers - all currently empty
\lhead{English B2}
\chead{Special Purposes Seminar: Freedom on the Internet}
\rhead{Team 3}

% Footers
\lfoot{}
\cfoot{}
\rfoot{\footnotesize Page \thepage\ of \pageref{LastPage}} % "Page 1 of 2"

\renewcommand{\headrulewidth}{0.0pt} % No header rule
\renewcommand{\footrulewidth}{0.4pt} % Thin footer rule

\usepackage{lettrine} % Package to accentuate the first letter of the text
\newcommand{\initial}[1]{ % Defines the command and style for the first letter
\lettrine[lines=3,lhang=0.3,nindent=0em]{
\color{DarkGoldenrod}
{\textsf{#1}}}{}}

%------------------------------------------------------------------------------
%	TITLE SECTION
%------------------------------------------------------------------------------

\usepackage{titling} % Allows custom title configuration

\newcommand{\HorRule}{\color{DarkGoldenrod} \rule{\linewidth}{1pt}} % Defines the gold horizontal rule around the title

\pretitle{\vspace{-30pt} \begin{flushleft} \HorRule \fontsize{50}{50} \usefont{OT1}{phv}{b}{n} \color{DarkRed} \selectfont} % Horizontal rule before the title

\title{Freedom \\
on the Internet} % Your article title

\posttitle{\par\end{flushleft}\vskip 0.5em} % Whitespace under the title

\preauthor{\begin{flushleft}\large \lineskip 0.5em \usefont{OT1}{phv}{b}{sl} \color{DarkRed}} % Author font configuration

\author{Wolf\,(s72785), Maxym\,(s72810), David\,(s72838) } % Your name

\postauthor{\footnotesize \usefont{OT1}{phv}{m}{sl} \color{Black} % Configuration for the institution name
Dresden University of Applied Sciences % Your institution

\par\end{flushleft}\HorRule} % Horizontal rule after the title

\date{} % Add a date here if you would like one to appear underneath the title block

%------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the title

\thispagestyle{fancy} % Enabling the custom headers/footers for the first page 

%------------------------------------------------------------------------------
%	ABSTRACT
%------------------------------------------------------------------------------

% The first character should be within \initial{}

\begin{onehalfspace}

\initial{S}ince summer 2013 the world is aware of illegal surveillance by \textit{state agencies} around the world violating fundamental human and civil rights justified by \textit{false claims} like child protection, copyright, drug policy and fighting terrorism.
Besides we all pay for this folly, most companies and individuals act just according to their financial intrests.
No doubt \textit{money is the main incentive} for criminals as well as for corporations that controle politicians nowadays.
In January 2009 a new kind of money was launched.
The network is the currency, transparent, pseudonymous, not eligible to direct regulation by banks nor governments. Remaining controversial it enables freedom and international transactions.
The Electronic Frontier Foundation started even earlier to implement an anonymity network: tor - the onion routing.
Our teams researched in the nets discovered that inventors built asymmetric cryptography with the most durable methods found at that time.
\textit{Blockchain technology} for the first time in history \textit{manages to solve the trust problem}.
Many people do not understand the technical matters or focus on their national currency only. That is why, by teaching about freedom in this seminar rather than capitalization, we want to make a difference and introduce technology that enables modern financial computing.
Use cases, that are adopted already by millions of users who care for their privacy and civil rights, will be presented.
We base our seminar on the scheme behind Bitcoin as described in the key paper by Satoshi Nakamoto. Moreover, we take a glance at the more accessible approach provided by Stellar in publications by the non-commercial company behind. The third source are texts that introduce the tor network.
%A selecttion of exercises consisting of crossword and listening to videos to start discussion
%
\textbf{still need to mention what kind of exercised we do}
%
\textit{Cryptography is no crime}. There can be \textit{no freedom without risk and responsibility}.
Now it is just the \textit{owners holding} the vital \textit{key} to control.

\end{onehalfspace}
%------------------------------------------------------------------------------

\end{document}
